### 2023-06-27 README.Rmd
Updated README intro paragraph Closes #117

## Description
```{r include = FALSE}
library(robvis)
```
The `robvis` package takes the summary table from risk-of-bias assessments and produces plots formatted according to the assessment tool used.

>>>>

## Description
```{r include = FALSE}
library(robvis)
```

The `robvis` (Risk-Of-Bias VISualization) package facilitates the rapid production of publication-quality risk-of-bias assessment figures, correctly formatted according to the assessment tool used.

The motivation for this package is more fully described in the (open access) article introducing the tool, available [here](https://doi.org/10.1002/jrsm.1411).
